Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-22 doc/thesis/latex/das_logs.tex

\appendix
\section{DAS Query logs}

\subsection*{Most common query patterns (from 2011-06-21 to 2012-10-01)}
\begin{verbatim}
total valid queries: 569,408
not well formed queries (e.g. free text or with typing mistakes): 98,923

50.16% (285605):	dataset dataset.name=?
13.54% (77071) :	site dataset.name=?
8.96%  (51035) :	file dataset.name=?
5.88%  (33504) :	run dataset.name=?
2.59%  (14739) :	release dataset.name=?
2.11%  (12036) :	config dataset.name=?
1.65%  (9420) 	:	dataset run.run_number=?
1.34%  (7642) 	:	block dataset.name=?
1.24%  (7084) 	:	dataset site.name=?
1.15%  (6562) 	:	dataset dataset.name=? release.name=?
1.10%  (6287) 	:	parent dataset.name=?
0.96%  (5488) 	:	file file.name=?
0.92%  (5245) 	:	dataset dataset.name=? status.name=?
0.77%  (4363) 	:	dataset release.name=?
0.75%  (4257) 	:	file dataset.name=? run.run_number=?
0.68%  (3874) 	:	run run.run_number=?
0.53%  (2994) 	:	site site.name=?
0.45%  (2576) 	:	site file.name=?
0.45%  (2556) 	:	dataset file.name=?
0.43%  (2438) 	:	lumi file.name=?
0.40%  (2282) 	:	dataset dataset.name=? site.name=?
0.35%  (1999) 	:	file block.name=?
0.35%  (1970) 	:	dataset dataset.name=? run.run_number=?
0.29%  (1640) 	:	group dataset.name=?
0.29%  (1631) 	:	lumi run.run_number=?
0.25%  (1402) 	:	child dataset.name=?
0.22%  (1268) 	:	run file.name=?
0.21%  (1204) 	:	block block.name=?
0.19%  (1088) 	:	release release.name=?
0.16%  (936) 	:	site block.name=?
0.12%  (703) 	:	file dataset.name=? lumi.number=? run.run_number=?
0.10%  (594) 	:	parent file.name=?
0.08%  (455) 	:	dataset block.name=?
0.06%  (365) 	:	dataset dataset.name=? datatype.name=? release.name=?
0.06%  (360) 	:	file dataset.name=? site.name=?

Interesting non-valid queries:
T!_CERN
*herwig*/AODSIM
--> keyword search
lumi file = (file dataset=/RelValProdTTbar/JobRobot-MC_42_V12_JobRobot-v1/GEN-SIM-RECO)
file,lumi dataset=/RelValProdTTbar/JobRobot-MC_42_V12_JobRobot-v1/GEN-SIM-RECO
--> Users may like more complex combined queries
file dataset=/MuEG/Run2011B-PromptReco-v1/AOD, file.size >1
file dataset=/MinimumBias/Run2010A-valskim-v6/RAW-RECO* | grep run between  [138923, 144086] 
--> Users mixing up the post and pre filters
\end{verbatim}
% 
% Possible keyword search test cases:
% run duration run_number between [195100,195200] 
%
% py dataset=/DYJetsToLL_M-50_TuneZ2Star_8TeV-madgraph-tarball/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM
%dataset dataset=*Run2011* datatype=data dataset=*RAW*

\appendix
\section{Data providers statistics}
\begin{verbatim}
(Some of the largest ones)

@@

Phedex: ~7GB, more often changes to existing (even old) records
    change rate: 2,359,934 file transfers last month (from site A to site B; 
                 change rate on the DB to be found out)
\end{verbatim}

>>>>

%\appendix
\begin{appendix}
\section{DAS Query logs (from 2011-06-21 to 2012-10-01)}

From the logs it can be seen that queries requiring heavy joins are quite common (100K queries through command line interface) that makes it worth investigating the possible performance optimizations.

\subsection{Common query patterns through Web browser}
total valid queries: 569,408
\\
not well formed queries (e.g. free text, typing mistakes, spam): 98,923

\begin{Verbatim}[commandchars=\\\{\},numbers=left,numbersep=4pt]
50.16% (285605)	:	dataset dataset.name=?
13.54% (77071)	:	site dataset.name=?
8.96%  (51035)	:	file dataset.name=?
5.88%  (33504)	:	run dataset.name=?
2.59%  (14739)	:	release dataset.name=?
2.11%  (12036)	:	config dataset.name=?
\textcolor{red}{1.65%  (9420) 	:	dataset run.run_number=?}
1.34%  (7642) 	:	block dataset.name=?
1.24%  (7084) 	:	dataset site.name=?
1.15%  (6562) 	:	dataset dataset.name=? release.name=?
1.10%  (6287) 	:	parent dataset.name=?
0.96%  (5488) 	:	file file.name=?
0.92%  (5245) 	:	dataset dataset.name=? status.name=?
0.77%  (4363) 	:	dataset release.name=?
\textcolor{red}{0.75%  (4257) 	:	file dataset.name=? run.run_number=?}
0.68%  (3874) 	:	run run.run_number=?
0.53%  (2994) 	:	site site.name=?
0.45%  (2576) 	:	site file.name=?
0.45%  (2556) 	:	dataset file.name=?
0.43%  (2438) 	:	lumi file.name=?
\textcolor{red}{0.40%  (2282) 	:	dataset dataset.name=? site.name=?}
0.35%  (1999) 	:	file block.name=?
0.35%  (1970) 	:	dataset dataset.name=? run.run_number=?
0.29%  (1640) 	:	group dataset.name=?
0.29%  (1631) 	:	lumi run.run_number=?
\end{Verbatim}

\begin{verbatim}
Interesting non-valid queries:
* keyword search: *herwig*/AODSIM
* Users may like more complex combined queries:
    lumi file = (file dataset=/RelValProdTTbar/JobRobot-MC_42_V12_JobRobot-v1/GEN-SIM-RECO)
    file,lumi dataset=/RelValProdTTbar/JobRobot-MC_42_V12_JobRobot-v1/GEN-SIM-RECO
* Users mixing up the post and pre filters:
    file dataset=/MuEG/Run2011B-PromptReco-v1/AOD, file.size >1
    file dataset=/MinimumBias/Run2010A-valskim-v6/RAW-RECO* | grep run between  [138923, 144086] 
\end{verbatim}
\newpage
\subsection{Common query patterns through Command Line\label{appendix_das_cli_logs}}
total valid queries: 6,9M\\
non valid queries: 76K

\begin{Verbatim}[commandchars=\\\{\},numbers=left,numbersep=4pt]
39.56% (2735728):	dataset dataset.name=?
22.80% (1576886):	dataset dataset.name=? status.name=?
12.49% (863636) :	file dataset.name=?
12.44% (860626) :	run run.run_number=?
4.60%  (318248) :	site dataset.name=?
2.18%  (150845) :	run dataset.name=?
\textcolor{red}{1.71%  (118404) :	file dataset.name=? run.run_number=?}\label{run_dataset_heavy}
1.32%  (90988)  :	file block.name=?
1.26%  (87266)  :	file file.name=?
0.50%  (34482)  :	block site.name=?
0.35%  (24049)  :	lumi file.name=?
0.25%  (17282)  :	release dataset.name=?
0.18%  (12556)  :	parent file.name=?
0.09%  (6341)   :	file dataset.name=? lumi.number=? run.run_number=?
\textcolor{red}{0.06%  (4306)   :	file dataset.name=? site.name=?}\label{site_dataset_distr_heavy}
0.05%  (3547)   :	dataset dataset.name=? primary_dataset.name=? release.name=? tier.name=?
0.05%  (3352)   :	dataset file.name=?
0.01%  (996)    :	parent dataset.name=?
0.01%  (755)    :	dataset site.name=?
\end{Verbatim}

% 
% Possible keyword search test cases:
% run duration run_number between [195100,195200] 
%
% py dataset=/DYJetsToLL_M-50_TuneZ2Star_8TeV-madgraph-tarball/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM
%dataset dataset=*Run2011* datatype=data dataset=*RAW*

\end{appendix}
\begin{appendix}
%\appendix
\section{Data providers statistics}
\begin{verbatim}
(Some of the largest ones)

@@

Phedex: ~7GB, more often changes to existing (even old) records
    change rate: 2,359,934 file transfers last month (from site A to site B; 
                 change rate on the DB to be found out)
\end{verbatim}
\end{appendix}

### 2012-10-22 doc/thesis/latex/literature_review.tex

In the setting of Boolean Keyword-based Retrieval over heterogeneous sources a keyword query could be translated into a ranked list of structured queries (similarly as \textit{SODA} system that propose SQL, \textit{Query Forms} approach that propose SQL templates or Keymantic trying to achieve this without accessing the data).
In the extreme case of having no control over a web-service that do not publish its contents, techniques like Google's Deep-web surfacing could index a subset of its contents enabling keyword search to some extent.

@@

\subsubsection*{What if there is no access to index data terms?}
\cite{Keymantic10, semantics_without_access} explores the case then there is no possibility to index the data terms, e.g. then a DB is behind a wrapper (e.g. accessible only through a \textit{Web form} in “Hidden Web” or \textit{a web-service}) then crawling is generally not possible.
%
In Keymantic\cite{Keymantic10} a keyword query is processed as follows: First, all keywords that  correspond to metadata items (e.g., field names) are extracted. The remaining keywords are considered as possible parameters to the input fields in the web form. Second, the likelihood of a remaining keyword to matching a metadata item is computed in order to rank different options of executing this keyword query on the "Hidden Web"\cite[p.942]{ethz2012}.

% See Appendix #1, for evaluation of they Demo system.

>>>>

In the setting of Boolean Keyword-based Retrieval over heterogeneous sources, a keyword query could be translated into a ranked list of structured queries (similarly as \textit{SODA} system that propose SQL, \textit{Query Forms} approach that propose SQL templates or Keymantic trying to achieve this without accessing the data).
In the extreme case of having no control over a web-service that do not publish its contents, techniques like Google's Deep-web surfacing could index a subset of its contents enabling keyword search to some extent.

@@

\subsubsection*{What if there is no access to index data terms?}
\cite{Keymantic10, semantics_without_access} explores the case then there is no possibility to index the data terms, e.g. then a DB is behind a wrapper (e.g. accessible only through a \textit{Web form} in “Hidden Web” or \textit{a web-service}) then crawling is generally not possible.
%
In Keymantic\cite{Keymantic10} a keyword query is processed as follows: First, all keywords that  correspond to metadata items (e.g., field names) are extracted. The remaining keywords are considered as possible parameters to the input fields in the web form. Second, the likelihood of a remaining keyword to matching a metadata item is computed in order to rank different options of executing this keyword query on the "Hidden Web"\cite[p.942]{ethz2012}. Because of no access to the actual data, results of this method were reported considerably worse on queries containing data terms, even if all metadata (e.g. business ontology) is given\cite{ethz2012}, therefore it is helpful to have at least some insight on the data behind a webservice.
% See Appendix #1, for evaluation of they Demo system.
